Spatial modelling of the electoral two-party preferred vote in Australia. A study of federal elections between 2001 and 2016 via the `eechidna` `R` package.

### 2019-03-27 04-results.Rmd
created the faceting of effects - 1 row for each variable. still have to get the limits to work (fixed for each variable)

### Diversity
In the lead up to the 2001 election, the Liberal government (in power) refused permission for the MV Tampa, a ship carrying 433 rescued refugees and 5 crew to enter Australian waters. This, along with the 9/11 attacks, were two key issues that are widely believed to have pushed the Liberal party to victory. In this 2001 election, electorates with a higher proportion of people speaking languages other than english at home (`OtherLanguageHome`) were significantly more likely to support Labor. This remains negative up until the 2016 election albeit insignificant. Higher proportions of people born in Asia (`Born_Asia`) is also significantly linked with Labor support in 2010, which may be due to refugee policy again arising as a key election issue in lead up to the election.

@@

>>>>

### Diversity
Larger migrant populations from Asia, the Middle East, South-Eastern Europe, the United Kingdom and elsewhere, are assocated with Labor support, or had no effect. Of these areas, only South-Eastern European populations were signficant in each election and Asian migrants were a significant in 2010. However, the effect of other languages (aside from English) is a far stronger effect, as observed through `OtherLanguageHome`. Surprisingly, electorates with more diverse speech were more likely to support the Liberal party from 2004 onwards, with this effect being significant in 2007, 2010 and 2016.

Of the variables relating to religion, only Judaism shows a consistent effect, with electorates with larger Jewish populations more likely to vote Liberal.

@@

```{r plotbornasia, fig.cap = "Effect of Born_Asia", out.width="60%", eval = F}
p <- grid_visreg("Born_Asia", xvar_title = "Born_Asia", xlimits = c(-0.9, 5), ylimits = c(20, 70), plot = T)
```

```{r plotjudaism, fig.cap = "Effect of Judaism", out.width="60%", eval = F}
p <- grid_visreg("Judaism", xvar_title = "Judaism", xlimits = c(-1.5, 3.8), ylimits = c(40, 70), plot = T)
```

### Partial residual plots

```{r}
vars_to_plot <- c("Judaism", "Born_Asia", "Born_SE_Europe", "OtherLanguageHome", "Education", "MedianAge", "DeFacto", "DiffAddress", "ManagerAdminClericalSales", "Transformative", "Extractive", "Unemployment", "Incomes")

ls_visreg <- list(Judaism = grid_visreg("Judaism"), Born_Asia = grid_visreg("Born_Asia"), Born_SE_Europe = grid_visreg("Born_SE_Europe"), OtherLanguageHome = grid_visreg("OtherLanguageHome"), Education = grid_visreg("Education"), MedianAge = grid_visreg("MedianAge"), DeFacto = grid_visreg("DeFacto"), DiffAddress = grid_visreg("DiffAddress"), ManagerAdminClericalSales = grid_visreg("ManagerAdminClericalSales"), Transformative = grid_visreg("Transformative"), Extractive = grid_visreg("Extractive"), Unemployment = grid_visreg("Unemployment"), Incomes = grid_visreg("Incomes"))

all_bands_df <- bind_rows(
  ls_visreg$Judaism$bands %>% mutate(varname = "Judaism", xmin = -1.5, xmax = 3.8),
  ls_visreg$Born_Asia$bands %>% mutate(varname = "Born_Asia", xmin = -0.9, xmax = 5.15),
  ls_visreg$Born_SE_Europe$bands %>% mutate(varname = "Born_SE_Europe", xmin = -0.85, xmax = 5.05),
  ls_visreg$OtherLanguageHome$bands %>% mutate(varname = "OtherLanguageHome", xmin = -1, xmax = 3.4),
  ls_visreg$Education$bands %>% mutate(varname = "Education", xmin = -1.3, xmax = 3),
  ls_visreg$MedianAge$bands %>% mutate(varname = "MedianAge", xmin = -2.55, xmax = 2.8),
  ls_visreg$DeFacto$bands %>% mutate(varname = "DeFacto", xmin = -2.2, xmax = 5.05),
  ls_visreg$DiffAddress$bands %>% mutate(varname = "DiffAddress", xmin = -2.2, xmax = 3.75),
  ls_visreg$ManagerAdminClericalSales$bands %>% mutate(varname = "ManagerAdminClericalSales", xmin = -3.75, xmax = 2.85),
  ls_visreg$Transformative$bands %>% mutate(varname = "Transformative", xmin = -2.3, xmax = 2.92),
  ls_visreg$Extractive$bands %>% mutate(varname = "Extractive", xmin = -0.75, xmax = 3.45),
  ls_visreg$Unemployment$bands %>% mutate(varname = "Unemployment", xmin = -2.08, xmax = 3.37),
  ls_visreg$Incomes$bands %>% mutate(varname = "Incomes", xmin = -1.5, xmax = 3.65)
)

all_points_df <- bind_rows(
  ls_visreg$Judaism$points %>% mutate(varname = "Judaism"),
  ls_visreg$Born_Asia$points %>% mutate(varname = "Born_Asia"),
  ls_visreg$Born_SE_Europe$points %>% mutate(varname = "Born_SE_Europe"),
  ls_visreg$OtherLanguageHome$points %>% mutate(varname = "OtherLanguageHome"),
  ls_visreg$Education$points %>% mutate(varname = "Education"),
  ls_visreg$MedianAge$points %>% mutate(varname = "MedianAge"),
  ls_visreg$DeFacto$points %>% mutate(varname = "DeFacto"),
  ls_visreg$DiffAddress$points %>% mutate(varname = "DiffAddress"),
  ls_visreg$ManagerAdminClericalSales$points %>% mutate(varname = "ManagerAdminClericalSales"),
  ls_visreg$Transformative$points %>% mutate(varname = "Transformative"),
  ls_visreg$Extractive$points %>% mutate(varname = "Extractive"),
  ls_visreg$Unemployment$points %>% mutate(varname = "Unemployment"),
  ls_visreg$Incomes$points %>% mutate(varname = "Incomes")
)

ggplot(data = all_bands_df %>% filter(varname %in% vars_to_plot[8:13])) +
  geom_ribbon(aes(x = variable, ymin = lower95, ymax = upper95), fill = "grey80") + 
  geom_point(aes(x = variable, y = part_res), data = all_points_df %>% filter(varname %in% vars_to_plot[8:13]), size = 0.75, col = "grey50") + 
  geom_line(aes(x = variable, y = fitted), col = "blue", size = 1) +
  theme_bw()+ 
  labs(x = varname, y = "Response") + 
  facet_wrap(varname ~ year, ncol = 6, scales = "free")

my_x_ranges <- range(range(model_df$Judaism), range(model_df$Born_Asia), range(model_df$Born_SE_Europe), range(model_df$OtherLanguageHome), range(model_df$Education), range(model_df$MedianAge), range(model_df$DeFacto), range(model_df$DiffAddress), range(model_df$ManagerAdminClericalSales), range(model_df$Transformative), range(model_df$Extractive), range(model_df$Unemployment), range(model_df$Incomes))

my_y_ranges <- range(
  range(c(ls_visreg$Judaism$bands$upper95, ls_visreg$Judaism$bands$lower95, ls_visreg$Judaism$points$part_res)),
  range(c(ls_visreg$Born_Asia$bands$upper95, ls_visreg$Born_Asia$bands$lower95, ls_visreg$Born_Asia$points$part_res)),
  range(c(ls_visreg$Born_SE_Europe$bands$upper95, ls_visreg$Born_SE_Europe$bands$lower95, ls_visreg$Born_SE_Europe$points$part_res)),
  range(c(ls_visreg$OtherLanguageHome$bands$upper95, ls_visreg$OtherLanguageHome$bands$lower95, ls_visreg$OtherLanguageHome$points$part_res)),
  range(c(ls_visreg$Education$bands$upper95, ls_visreg$Education$bands$lower95, ls_visreg$Education$points$part_res)),
  range(c(ls_visreg$MedianAge$bands$upper95, ls_visreg$MedianAge$bands$lower95, ls_visreg$MedianAge$points$part_res)),
  range(c(ls_visreg$DeFacto$bands$upper95, ls_visreg$DeFacto$bands$lower95, ls_visreg$DeFacto$points$part_res)),
  range(c(ls_visreg$DiffAddress$bands$upper95, ls_visreg$DiffAddress$bands$lower95, ls_visreg$DiffAddress$points$part_res)),
  range(c(ls_visreg$ManagerAdminClericalSales$bands$upper95, ls_visreg$ManagerAdminClericalSales$bands$lower95, ls_visreg$ManagerAdminClericalSales$points$part_res)),
  range(c(ls_visreg$Transformative$bands$upper95, ls_visreg$Transformative$bands$lower95, ls_visreg$Transformative$points$part_res)),
  range(c(ls_visreg$Extractive$bands$upper95, ls_visreg$Extractive$bands$lower95, ls_visreg$Extractive$points$part_res)),
  range(c(ls_visreg$Unemployment$bands$upper95, ls_visreg$Unemployment$bands$lower95, ls_visreg$Unemployment$points$part_res)),
  range(c(ls_visreg$Incomes$bands$upper95, ls_visreg$Incomes$bands$lower95, ls_visreg$Incomes$points$part_res))
  )

ggplot(data = all_bands_df %>% filter(varname %in% vars_to_plot[12:13])) +
  geom_ribbon(aes(x = variable, ymin = lower95, ymax = upper95), fill = "grey80") + 
  geom_point(aes(x = variable, y = part_res), data = all_points_df %>% filter(varname %in% vars_to_plot[12:13]), size = 0.75, col = "grey50") + 
  geom_line(aes(x = variable, y = fitted), col = "blue", size = 1) +
  theme_bw() + 
  labs(x = varname, y = "Response") + 
  facet_wrap(varname ~ year, ncol = 6, scales = "free") +
  expand_limits(x = my_x_ranges[23:26], y = my_y_ranges[23:26])

# https://stackoverflow.com/questions/18046051/setting-individual-axis-limits-with-facet-wrap-and-scales-free-in-ggplot2
